### 2020-02-06 README.Rmd

```{r eval = FALSE, echo = FALSE}
[![Travis-CI Build Status](https://travis-ci.org/geanders/hurricaneexposure.svg?branch=master)](https://travis-ci.org/geanders/hurricaneexposure)
```

@@

- Anderson B, Yan M, Ferreri J, Crosson W, Al-Hamdan M, Schumacher A and
 Eddelbuettel D (2017). _hurricaneexposure: Explore and Map County-Level
 Hurricane Exposure in the United States_. R package version 0.0.1, <URL:
 http://CRAN.R-project.org/package=hurricaneexposure>.

- Anderson B, Schumacher A, Crosson W, Al-Hamdan M, Yan M, Ferreri J, Chen Z,
 Quiring S and Guikema S (2017). _hurricaneexposuredata: Data Characterizing
 Exposure to Hurricanes in United States Counties_. R package version 0.0.1,
 <URL: https://github.com/geanders/hurricaneexposuredata>.

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(tidyr)
hurr_tracks %>%
        select(storm_id) %>%
        distinct() %>%
        separate(storm_id, into = c("storm_name", "Year"), sep = "-") %>%
        group_by(Year) %>%
        summarize(Storms = paste(storm_name, collapse = ", ")) %>%
        mutate(Distance = "x",
               Wind = "x",
               Rain = ifelse(Year <= 2011, "x", ""),
               Flood = ifelse(Year >= 1996, "x", ""),
               Tornado = "x") %>%
        pander::pander(justify = "clccccc")
```

>>>>

@@

- Anderson B, Yan M, Ferreri J, Crosson W, Al-Hamdan M, Schumacher A and
 Eddelbuettel D (2020). _hurricaneexposure: Explore and Map County-Level
 Hurricane Exposure in the United States_. R package version 0.1.1, <URL:
 http://CRAN.R-project.org/package=hurricaneexposure>.

- Anderson B, Schumacher A, Crosson W, Al-Hamdan M, Yan M, Ferreri J, Chen Z,
 Quiring S and Guikema S (2020). _hurricaneexposuredata: Data Characterizing
 Exposure to Hurricanes in United States Counties_. R package version 0.1.0,
 <URL: https://github.com/geanders/hurricaneexposuredata>.

@@

```{r echo = FALSE, message = FALSE, warning = FALSE}
library(dplyr)
library(tidyr)
library(stringr)
hurr_tracks %>%
        select(storm_id) %>%
        distinct() %>%
        mutate(Year = str_extract(storm_id, "-[0-9].+"),
               Year = str_remove(Year, "-"),
               storm_name = str_remove(storm_id, "-[0-9].+")) %>% 
        group_by(Year) %>%
        summarize(Storms = paste(storm_name, collapse = ", ")) %>%
        mutate(Distance = "x",
               Wind = "x",
               Rain = ifelse(Year <= 2011, "x", ""),
               Flood = ifelse(Year >= 1996, "x", ""),
               Tornado = "x") %>%
        pander::pander(justify = "clccccc")
```
